---
title: MRSI
output: rmarkdown::github_document
---
<!-- RENDER:
  rstudio: ctrl+shift+k (or play icon)
  emacs: polymode, poly-r, ess: M-n w (poly-weave)
  R: rmarkdown::render("results.rmd")
-->

```{r, echo = FALSE}
# require rmarkdown for sweave/knittr
knitr::opts_chunk$set(fig.path = "figs/")
require(dplyr)
require(tidyr)
require(glue)
require(ggplot2)
require(lme4)
source('funcs.R')
```
# MRSI
9x9x10mm voxel position interactively for all regions of interest. Voxel metabolite concentrations estimated by LCModel.

## Input
 * metabolite concentration per voxel from `data/13MP20200207_LCMv2fixidx.csv`.
 * Spectrum that failed visual inspection annotated in `data/lcm_bad_visual_qc.txt`.

```{r, echo=FALSE}
system("wc -l data/* |sed '$d'", intern=T) %>% paste(collapse="\n") %>% cat
```

### limiting

We exclude spectrum that failed visual inspection, extranous data (non-ROI voxels), poor model fit (high "SD")

```{r, echo=FALSE}

MRS_all     <- read_mrsi_roi()
MRS_qc      <- remove_bad_qc(MRS_all)
MRS_visit1  <- visit1_and_data(MRS_qc)
MRS_cleaned <- remove_major_met_outliers(MRS_visit1)


quick_info <- function(d, stage=NULL)
    data.frame(nsubj=length(unique(gsub('_.*','',d$ld8))),
               nvisits=length(unique(d$ld8)), 
               nrow=nrow(d))
exclusion_df <- list(all=MRS_all, "visual qc"=MRS_qc, "visit1 only"=MRS_visit1, "rm SD outlier"=MRS_cleaned) %>%
    lapply(quick_info) %>%
    bind_rows(., .id="stage")

knitr::kable(exclusion_df)

# better as a table
#exclusion_df %>% gather(of,n,-stage) %>%
#    ggplot() + aes(x=stage, y=n, color=of) +
#    geom_point() + facet_grid(of~., scales="free_y") + cowplot::theme_cowplot()
```
### Demographics
```{r age-distribution}
id_summary <- MRS_cleaned %>% group_by(ld8,age,sex) %>% tally # n=number of ROIs, ignored
ggplot(id_summary, aes(x=age, fill=sex)) +
    geom_histogram(color="black", binwidth = 1) +
    theme_classic(base_size = 15) +
    xlab("Age (years)") + ylab("Count") + labs(fill = "Sex") + 
    ggtitle("Age Distribution")
```


### inverse and quadratic age
Though using linear models, we can model inverse or quadratic chanes in age.
```r
MRS <- add_inv_and_quad_age(MRS_cleaned)
```

## Models
One outlier removal strategy is to remove metabolite concentrations that are 2 standard deviations from the mean.
Another is to remove poor model fit. For most metabolites this is a CRLB ("SD") above `20`. Model input will not include these outlier values. 
```{r}
z_thres <- 2
```


### Glu
```{r child= 'model-glu.Rmd'}
```

